### 2020-06-07 ArticleAcortado.tex
d

\newlength{\margen}
\setlength{\margen}{\paperwidth}
\addtolength{\margen}{-\textwidth}
\addtolength{\skip\footins}{0.7 cm}
\setlength{\margen}{0.5\margen}
\addtolength{\margen}{-1in}
\setlength{\oddsidemargin}{\margen}
\setlength{\evensidemargin}{\margen}
\setlength{\abovedisplayskip}{3pt}
\setlength{\belowdisplayskip}{3pt}
%%%% Small setup %%%%
\hypersetup{
	colorlinks=false,
	pdfborder={1 1 0.0005},
}
\setlength{\parskip}{0.2cm}
%%%%%%%%%%%%%%%
\usepackage{tikz-cd}
\usetikzlibrary{cd}
\usepackage[english]{babel}
\usepackage{todonotes}
\usepackage{cleveref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{bbding}
\usepackage{tcolorbox}
\usepackage{natbib}

@@

\begin{document}
\begin{abstract}
	We extend the convergence law for sparse random graphs proven
	by Lynch to arbitrary relational languages.
	We consider a finite relational vocabulary $\sigma$
	and a first order theory $T$ for $\sigma$ 
    composed of symmetry and 
    anti-reflexivity axioms. We define a binomial random model of finite 
    $\sigma$-structures that satisfy $T$ and show that first order properties have 
    well defined asymptotic probabilities when the expected number of tuples satisfying
    each relation in $\sigma$ is linear.
    It is also shown that those limit probabilities are well-behaved with
    respect to some parameters that represent the density of tuples satisfying $R$
    for each relation $R$ in the vocabulary $\sigma$. 
    An application of these results to the problem of random Boolean 
    satisfiability is presented afterwards. 
    We show that in a random $k$-CNF formula over $n$ variables where
    each possible clause occurs with probability $\sim c/n^{k-1}$ independently any 
    first order property of $k$-CNF formulas that
    implies unsatisfiability does almost surely not hold as $n$ tends to infinity.

@@

We say that a sequence of random structures $\{G_n\}_n$ satisfies a limit
law with respect to some logical language $L$ if for any property $P$ expressible in
$L$ the probability that $G_n$ satisfies $P$ tends to some limit as $n$ goes to $\infty$.
If that limit takes only the values zero and one then we say that $\{G_n\}_n$ satisfies
a zero-one law with respect to $L$.  
Convergence and zero one laws have been extensively studied with regards to 
random binomial graphs $G(n,p)$.
The seminal theorem on this topic, due to Fagin \cite{fagin1976probabilities}
and Glebskii et al. \cite{glebskii1969range} independently, 
concerns general relational structures.
When applied to graphs it states that if $p$ is a fixed probability
then $G(n,p)$ satisfies a zero-one law with respect to the first order
(FO) language of graphs. This zero-one law was later extended by Shelah and Spencer
in \cite{shelah1988zero}. There it is proven, among other results,
that if $p:=p(n)$ was a decreasing function on
$n$ of the form $n^{-\alpha}$, and $\alpha\in (0,1)$ is irrational
then $G(n,p(n))$ obeys a zero-one law with respect to FO logic. Moreover, 
it is also proven that if $\alpha\in (0,1)$ is rational then $G(n,p(n))$ 
does not obey a convergence law. This was further extended by Lynch
in \cite{lynch1992probabilities}, where it is shown that in the
case where the expected number of edges is linear, when $p(n)\sim \beta/n$
for some $\beta\in (0,\infty)$, then $G(n,p(n))$ satisfies a limit law with
respect to FO logic. The following is a restatement of the main theorem
in that article.

\begin{theorem*}
	Let $p(n)\sim \beta/n$. For any FO sentence $\phi$, the function
	$F_\phi: (0,\infty)\rightarrow [0,1]$ given by 
	\[ F_\phi(\beta) = \Ln \mathrm{Pr}\left( \mathrm{G}(n,p(n))
	\text{ satisfies } \phi   \right) \]
	is well defined and is given by an expression with parameter $\beta$ built
	using rational constants, addition, multiplication and exponentiation with base $e$.
\end{theorem*}

A relevant aspect of this result is that the limit probability of any FO
property in $G(n,p(n))$ when $p(n)\sim \beta/n$ varies analytically with $\beta$.
A consequence of this is that in this conditions no FO property can "capture" sudden changes 
in the structure of $G(n,p(n))$. \par
It was left open at the end of \cite{lynch1992probabilities} whether the convergence law obeyed
by $G(n,p(n))$in the range $p(n)\sim \beta/n$
could be generalized for other random models of relational structures 
that contain relations of degree greater than $2$.
A result in this regard was obtained in \cite{salvadorbrasil}, 
among other zero-one and convergence laws.
There it is considered $G^d(n,p)$ the random model of $d$-uniform hypergraphs where
each $d$-edge is added to a set of $n$ labeled vertices with probability $p$ independently.
It is shown that when $p(n)\sim \beta/n^{d-1}$ -i.e., when the expected number of
edges is linear- then $G^d(n,p(n))$ obeys a convergence law with respect of the FO
language of $d$-uniform hypergraphs. With little additional work it can be shown that
in this conditions the limit probability of any FO property of $G^d(n,p(n))$ varies 
analytically with $\beta$. We 
extend this result to arbitrary relational structures
to whose relations we can impose symmetry and anti-reflexivity constraints 
(\cref{thm:main}). \par

This generalization is motivated by an application to the problem of random 
satisfiability. We continue the study started by Atserias in \cite{atserias2005definability}
with regards to the definability in first order logic of certificates for unsatisfiability
that hold for typical unsatisfiable formulas. There it is considered a random model for
$3$-CNF formulas where each possible clause over $n$ variables is added with probability $p$ 
independently. This way the expected number of clauses is $\Theta(n^3p)$ as $n$ grows.
The main result of that article states that when the expected number of clauses is
$\Theta(n^{2+\alpha})$ for any arbitrary $\alpha>0$ then there exists some 
FO property of $3$-CNF formulas that implies
unsatisfiability and asymptotically almost surely (a.a.s) holds for unsatisfiable formulas. 
Furthermore, if the expected number of clauses is $\Theta(n^{2-\alpha})$ for any irrational
$\alpha>0$ then no FO property that implies unsatisfiability holds a.a.s
for unsatisfiable formulas. We complement this result by showing that 
in a random $l$-CNF formula were each clause over $n$ variables is chosen  
with probability $p(n)$ independently when the expected number of clauses is 
$\Theta(n)$ there is no FO property that certifies unsatisfiability and
holds a.a.s for unsatisfiable formulas (\cref{thm:mainsat}).

@@

We will use the convention that over-lined variables
, like $\overline{x}$, denote ordered tuples of arbitrary length.
Given an ordered tuple $\overline{x}$
we define the number $len(\overline{x})$ as its length. 
Given a tuple $\overline{x}$ and an element $x$ the expression
$x\in \overline{x}$ means that $x$ appears as some coordinate
in $\overline{x}$. 
Given a map $f:X\rightarrow Y$ between two sets $X, Y$ and 
an ordered tuple $\overline{x}:=(x_1,\dots,x_a)\in X^*$ 
we define $f(\overline{x})\in Y^*$ as the tuple 
$(f(x_1),\dots,f(x_a))$.
Given two tuples $\overline{x},\overline{y}$
we write $\overline{x}^\smallfrown \overline{y}$ to denote their 
concatenation.
\par

Let $S$ be a set, $a$ a positive natural number, 
and $\Phi$ a group of permutations over 
$[a]$. Then $\Phi$ acts naturally over
$S^a$ in the following way: Given $g\in \Phi$ and
$\overline{x}:=(x_1,\dots,x_a)\in S^a$ we define 
$g\cdot \overline{x}$ 
as the tuple $(x_{g(1)},\dots,x_{g(a)})$. 
We will denote by $S^a/\Phi$ to the quotient
of the set $S^a$ by this action. Given an element
$\overline{x}:=(x_1,\dots, x_a)\in S^a$ we will denote its equivalence
class in $S^a/\Phi$ by $[x_1,\dots,x_a]$ or $[\overline{x}]$.
Thus, for any
$g\in \Phi$, by definition $[x_1,\dots,x_a]=[x_{g(1)}
,\dots,x_{g(a)}]$. \par
The notations $\overline{x}$ and
$(x_1,\dots, x_a)$ 
will be reserved 
to ordered tuples while 
$[\overline{x}]$ and
$[x_1,\dots,x_a]$ will denote ordered tuples modulo the
action of some arbitrary group of permutations. Which group is
this will depend on the ambient set where $[x_1,\dots,x_a]$ belongs
and it should either be clear from context or not be relevant.\par

Given two real functions over the natural numbers 
$f,g:\N \rightarrow \R$ we will write $f=O(g)$ to 
mean that there exists some constant $C\in \R$
such that $f(n)\leq Cg(n)$ for $n$ sufficiently large, 
as usual. We will write $f=\Theta(g)$ if both $f=O(g)$ and
$g=O(f)$. If $g(n)\neq 0$ for $n$ large enough then
we will write $f\sim g$ when $\Ln \frac{f(n)}{g(n)}=1$.

%%\todo[inline]{Añadir referencias y trabajo relacionado con random SAT}
%

\subsection{Logical preliminaries}
We assume familiarity with first order logic (FO). We follow 
the convention that first order logic contains the equality symbol. 
Given a vocabulary $\sigma$ we will denote by $FO[\sigma]$ the set of 
first order formulas of vocabulary $\sigma$. We define the set of 
\textbf{free variables} of a formula as usual. 
Given a relation symbol $R\in \sigma$ we denote by $ar(R)$ the arity of $R$. 
Given a formula $\phi\in FO[\sigma]$ we will use the notation $\phi(\overline{y})$ 
to express that $\overline{y}$ is a tuple of 
(different) variables which contains all free variables in $\phi$ and
none of its bounded variables, but it may contain variables
which do not appear in $\phi$.
Formulas with no free variables are called \textbf{sentences} and 
formulas with no quantifiers are called \textbf{open formulas}.

@@

We define the \textbf{excess} $ex(G)$ of an hypergraph $G$ as the number
\[
ex(G):= \left(\sum_{R\in \sigma} (ar(R)-1)|E_R(G)|\right) - |V(G)|.  
\] 
That is, the excess of $G$ is its "weighted number of edges"
minus its number of vertices. \par
An hypergraph $G$ is \textbf{connected} if for any two vertices $v,u\in V(G)$
there is a sequence of edges $e_1,\dots, e_m\in E(G)$ such that
$v\in V(e_1), u\in V(e_m)$ and for each $i\in [m-1]$, 
$V(e_i)\cap V(e_{i+1})\neq \emptyset$. It holds that
$ex(G)\geq -1$ for any connected hypergraph.
\par
Given an hypergraph $G$ we define the following metric, $d$, over $V(G)$:
\[ d^G(u,v)= \min_{\substack{H \subset G\\ 
		H \text{ connected }\\
		u,v\in V(H)}} |E(H)| .\]
That is, the \textbf{distance} between $v$ and $u$ is the minimum number of
edges necessary to connect $v$ and $u$. 
If such number does not exist we define $d^G(u,v)=\infty$. 
When $G$ 
is understood or not relevant we will usually simply denote the 
distance by $d$ instead of $d^G$. Equivalently, the distance $d$
coincides with the usual one defined over the Gaifman graph of the structure 
$G$. The \textbf{diameter} of an hypergraph is the maximum distance between any 
two of its vertices. 
We extend naturally the distance $d$ to sets and tuples of
vertices, as usual. Given a vertex/set/tuple $X$ and a number
$r\in \N$ we define the \textbf{neighborhood}
$N^G(X;r)$, or simply $N(X;r)$ when $G$ is not relevant,
as the set of vertices $v$ such that $d^G(X,v)\leq r$.
\par
A connected hypergraph $G$ is a path between two of its 
vertices $v,u\in V(G)$ if $G$ 
does not contain any connected proper sub-hypergraph containing both $v,u$.
\par
A connected hypergraph $G$ is a \textbf{tree} if $ex(G)=-1$ and \textbf{dense} if $ex(G)>0$.
An hypergraph is called $r$-\textbf{sparse} if it does not contain any dense sub-hypergraph $H$
such that $diam(H)\leq r$.
A connected hypergraph $G$ with $ex(G)\geq 0$ is called \textbf{saturated} 
if for any non-empty proper sub-hypergraph
$H\subset G$ it holds $ex(H)<ex(G)$. 
A connected hypergraph $G$ with $ex(G)=0$ is called \textbf{unicycle}. 
A saturated unicycle is called a \textbf{cycle}. \par
A \textbf{rooted tree} $(T,v)$ is a tree $T$ with a 
distinguished vertex $v\in V(T)$ called its \textbf{root}.
We will usually omit the root when it is not relevant and 
write just $T$ instead of $(T,v)$. The
\textbf{initial edges} of a rooted tree $(T,v)$ are 
the edges in $T$ that contain $v$. 
We define the radius of a rooted tree
as the maximum distance between its root
and any other vertex.
\par

@@

\textbf{Isomorphisms} between hypergraphs are defined the same as 
isomorphisms between relational structures. Isomorphisms between $\Sigma$-hypergraphs are just
isomorphisms between the underlying hypergraphs that also preserve their colorings. 
In both cases we denote the isomorphism relation by $\simeq$. 
Given an hypergraph $H$, resp. a $\Sigma$-hypergraph $(H, \chi)$,
an \textbf{automorphism} of $H$, resp. $(H,\chi)$,
is an isomorphism from $H$, resp $(H,\chi)$ to itself.
We will denote by $\aut(H)$, resp. $\aut(H,\chi)$
 the number of such automorphisms. \par

Let $H$ be an hypergraph and let $V$ be a set. We define the
set of \textbf{copies of $H$ over $V$}, denoted as $Copies(H,V)$, 
as the set of hypergraphs 
$H^\prime$ such that
$V(H^\prime)\subset V$ and $H\simeq H^\prime$. Let 
$\chi$ be a $\Sigma$-coloring of $H$. 
As before, we define the set $Copies\left(
(H,\chi),\, \, V\right)$ as the set of $\Sigma$-hypergraphs
$(H^\prime,\chi^\prime)$ satisfying $V(H^\prime)\subset V$ and
$(H,\chi)\simeq (H^\prime,\chi^\prime)$. Let $\mathbb{H}$ be 
an isomorphism class of $\Sigma$-hypergraphs. Then the set
$Copies(\mathbb{H}, V)$ is defined as the set of $\Sigma$-hypergraphs
$(H^\prime,\chi^\prime)$ such that 
$V(H^\prime)\subset V$ and
$(H^\prime,\chi^\prime)\in \mathbb{H}$. 
Let $v\in V$ and $s\in \Sigma$. We define the
set $Copies\left(\mathbb{H}, V;\,\, (v,s)\right)$ 
as the set of $\Sigma$-hypergraphs
$(H^\prime,\chi^\prime)\in Copies(\mathbb{H}, V)$
that satisfy $v\in V(H^\prime)$ as well as
$\chi^\prime(v)=s$. \par

Given $\mathbb{H}$ an isomorphism class of hypergraphs or $\Sigma$-hypergraphs
, we define expressions
such as $ex(\mathbb{H})$, $\aut(\mathbb{H})$,
$|V(\mathbb{H})|$, $|E(\mathbb{H})|$ or
$Copies(\mathbb{H},V)$ via representatives of $\mathbb{H}$.\par

@@

\begin{definition}

@@

\begin{definition}
	Let $\Sigma_{(k,r-1)}$ be the set of $\sim_k$ classes
	of rooted trees with radii at most $r-1$. Then
	we call a $(k,r)$-\textbf{cycle} to an isomorphism class
	of $\Sigma_{(k,r-1)}$-hypergraphs 
	$(H,\tau)$ that are cycles of diameter at most $2r+1$.
	We will denote by $C(k,r)$ the set of $(k,r)$-cycles.
\end{definition}

>>>>

\newlength{\margen}
\setlength{\margen}{\paperwidth}
\addtolength{\margen}{-\textwidth}
\addtolength{\skip\footins}{0.7 cm}
\setlength{\margen}{0.5\margen}
\addtolength{\margen}{-1in}
\setlength{\oddsidemargin}{\margen}
\setlength{\evensidemargin}{\margen}
\setlength{\abovedisplayskip}{3pt}
\setlength{\belowdisplayskip}{3pt}
%%%% Small setup %%%%
\hypersetup{
	colorlinks=false,
	pdfborder={1 1 0.0005},
}
\setlength{\parskip}{0.2cm}
%%%%%%%%%%%%%%%
\usepackage{tikz-cd}
\usetikzlibrary{cd}
\usepackage[english]{babel}
\usepackage{todonotes}
\usepackage{cleveref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{bbding}
\usepackage{tcolorbox}
\usepackage[square,numbers]{natbib}

@@

\begin{document}
\begin{abstract}
	We extend the convergence law for sparse random graphs proven
	by Lynch to arbitrary relational languages.
	We consider a finite relational vocabulary $\sigma$
	and a first order theory $T$ for $\sigma$ 
    composed of symmetry and 
    anti-reflexivity axioms. We define a binomial random model of finite 
    $\sigma$-structures that satisfy $T$ and show that first order properties have 
    well defined asymptotic probabilities when the expected number of tuples satisfying
    each relation in $\sigma$ is linear.
    It is also shown that those limit probabilities are well-behaved with
    respect to some parameters that represent the density of tuples each relation $R$ 
    in the vocabulary $\sigma$. 
    An application of these results to the problem of random Boolean 
    satisfiability is presented afterwards. 
    We show that in a random $k$-CNF formula over $n$ variables where
    each possible clause occurs with probability $\sim c/n^{k-1}$ independently any 
    first order property of $k$-CNF formulas that
    implies unsatisfiability does almost surely not hold as $n$ tends to infinity.

@@

We say that a sequence of random structures $\{G_n\}_n$ satisfies a limit
law with respect to some logical language $L$ if for any property $P$ expressible in
$L$ the probability that $G_n$ satisfies $P$ tends to some limit as $n$ goes to $\infty$.
If that limit takes only the values zero and one then we say that $\{G_n\}_n$ satisfies
a zero-one law with respect to $L$.  \par
Convergence and zero one laws have been extensively studied with regards to 
random binomial graphs $G(n,p)$.
The seminal theorem on this topic, due to Fagin \cite{fagin1976probabilities}
and Glebskii et al. \cite{glebskii1969range} independently, 
concerns general relational structures.
When applied to graphs it states that if $p$ is a fixed probability
then $G(n,p)$ satisfies a zero-one law with respect to the first order
(FO) language of graphs. \par
This zero-one law was later extended by Shelah and Spencer
in \cite{shelah1988zero}. There it is proven, among other results,
that if $p:=p(n)$ was a decreasing function on
$n$ of the form $n^{-\alpha}$, and $\alpha>0$ is irrational
then $G(n,p(n))$ obeys a zero-one law with respect to FO logic. Moreover, 
it is also proven that if $\alpha\in (0,1)$ is rational then $G(n,p(n))$ 
does not obey a convergence law. \par
This was further extended by Lynch
in \cite{lynch1992probabilities}, where it is shown that in the
case where the expected number of edges is linear, when $p(n)\sim \beta/n$
for some $\beta\in (0,\infty)$, then $G(n,p(n))$ satisfies a limit law with
respect to FO logic. The following is a restatement of the main theorem
in that article.

\begin{theorem*}[Lynch, 1992]
	Let $p(n)\sim \beta/n$. For any FO sentence $\phi$, the function
	$F_\phi: (0,\infty)\rightarrow [0,1]$ given by 
	\[ F_\phi(\beta) = \Ln \mathrm{Pr}\left( \mathrm{G}(n,p(n))
	\text{ satisfies } \phi   \right) \]
	is well defined and is given by an expression with parameter $\beta$ built
	using rational constants, addition, multiplication and exponentiation with base $e$.
\end{theorem*}

A relevant aspect of this result is that the limit probability of any FO
property in $G(n,p(n))$ when $p(n)\sim \beta/n$ varies analytically with $\beta$.
A consequence of this is that in these conditions no FO property can "capture" sudden changes 
in the structure of $G(n,p(n))$. \par
It was left open at the end of \cite{lynch1992probabilities} whether the convergence law obeyed
by $G(n,p(n))$in the range $p(n)\sim \beta/n$
could be generalized for other random models of relational structures 
that contain relations of arity greater than $2$.
A result in this regard was obtained in \cite{salvadorbrasil}, 
among other zero-one and convergence laws.
There $G^d(n,p)$ is considered, the random model of $d$-uniform hypergraphs where
each $d$-edge is added to a set of $n$ labeled vertices with probability $p$ independently.
It is shown that when $p(n)\sim \beta/n^{d-1}$ -i.e., when the expected number of
edges is linear- then $G^d(n,p(n))$ obeys a convergence law with respect of the FO
language of $d$-uniform hypergraphs. With little additional work it can be shown that
in these conditions the limit probability of any FO property of $G^d(n,p(n))$ varies 
analytically with $\beta$. We 
extend this result to arbitrary relational structures
to whose relations we can impose symmetry and anti-reflexivity constraints 
(\cref{thm:main}). \par

This generalization is motivated by an application to the problem of random 
satisfiability. We continue the study started by Atserias in 
\cite{atserias2005definability}
with regards to the definability in first order
logic of certificates for unsatisfiability
that hold for typical unsatisfiable formulas. 
A random model for $3$-CNF formulas where 
each possible clause over $n$ variables 
is added with probability $p$ independently is considered there.
This way the expected number of clauses $m$ is $\Theta(n^3p)$ as $n$ grows.
The main result of that article states the following:
(1) if $m=\Theta(n^{2-\alpha})$ 
for any irrational $\alpha>0$, then no FO property of $3$-CNF formulas
that implies unsatisfiability holds asymptotically almost surely (a.a.s) 
for unsatisfiable formulas, and (2) if $m=\Theta(n^{2+\alpha})$ for any $\alpha>0$,
then there exists some FO property that implies
unsatisfiability and  holds a.a.s for unsatisfiable formulas. \par
The second part of the statement is the simpler one to prove:
it can be shown that when $m=\Theta(n^{2+\alpha})$ for some 
$\alpha>0$ then the random $3$-CNF formula
a.a.s contains some fixed unsatisfiable subformula (which depends
on the choice of $\alpha$). This is clearly expressible in FO logic, 
so (2) follows. The proof of (1) is more involved and, in fact, 
shows something stronger: if $m=\Theta(n^{2-\alpha})$
for any $\alpha>0$ irrational, then all FO properties 
that imply unsatisfiability
a.a.s do not hold. This proof employs
techniques based in the ones used by Shelah and Spencer 
in \cite{shelah1988zero} to prove that $G(n,p)$ satisfies a 
zero-one law with respect to FO logic when $p$ is an irrational 
power of $n$. \par
Since the techniques used to prove (2) rely in the fact that $\alpha$
is irrational, the study of the range $m=\Theta(n)$
(that is, $m=\Theta(n^{2-\alpha})$ with $\alpha=1$), was left open.
This range is of special interest because it is where the phase 
transition from almost sure satisfiability to almost sure unsatisfiability
takes place. It was shown
in \cite{chvatal1992mick} that a random $k$-CNF formula with
$m$ clauses over $n$ variables satisfying that $m\sim c\cdot n$ 
is a.a.s satisfiable for all sufficiently small values of $c$ and is a.a.s
unsatisfiable for all sufficiently big values of $c$.
\par
The possibility of studying FO definability of certificates for unsatisfiability
in random $l$-CNF formulas with a linear expected number of clauses 
using a generalization of Lynch's theorem was suggested by Atserias. 
This application is discussed in \cref{sec:SAT}. We give a brief overview
of it here. Let $F(l,n,p)$ be a random model of $l$-CNF 
formulas where each $l$-clause over $n$ variables is chosen with probability
$p$ independently. Let $F_n(\beta)$ denote a random formula in
$F(l,n,p)$ where $p:=p(n)\sim \beta/n^{l-1}$. 
Suppose that 
every FO property of $l$-CNF formulas 
has a well defined asymptotic probability in $F_n(\beta)$
for any $\beta>0$.
Further suppose that those asymptotic probabilities vary analytically
with $\beta$. Then any FO property that implies unsatisfiability
a.a.s does not hold in $F_n(\beta)$ for any
$\beta>0$. Indeed, let $P$ be one of such FO properties. One can find a
value $\beta_0>0$ satisfying that 
a.a.s $F_n(\beta)$ is satisfiable when $0<\beta<\beta_0$.
In consequence $P$ a.a.s does not hold
in $F_n(\beta)$ when $0<\beta<\beta_0$.
Since the asymptotic probability of $P$ varies analytically
with $\beta$ and it vanishes in the non-empty interval $(0,\beta_0)$,
because of the Principle of Analytical Continuation
it must be true that a.a.s $P$ does not hold in $F_n(\beta)$ for all
$\beta>0$.

@@

We will use the convention that over-lined variables
, like $\overline{x}$, denote ordered tuples of arbitrary length.
Given an ordered tuple $\overline{x}$
we define the number $len(\overline{x})$ as its length. 
Given a tuple $\overline{x}$ and an element $x$ the expression
$x\in \overline{x}$ means that $x$ appears as some coordinate
in $\overline{x}$. 
Given a map $f:X\rightarrow Y$ between two sets $X, Y$ and 
an ordered tuple $\overline{x}:=(x_1,\dots,x_a)\in X^*$ 
we define $f(\overline{x})\in Y^*$ as the tuple 
$(f(x_1),\dots,f(x_a))$.
Given two tuples $\overline{x},\overline{y}$
we write $\overline{x}^\smallfrown \overline{y}$ to denote their 
concatenation. Given a set $S$ and elements $x_s$ for each $s\in S$
we will write $\{x_s\}_{s\in S}$, or just $\{x_s\}_s$ when $S$ is understood,
to denote the tuple indexed by $S$ which for any $s\in S$
contains the element $x_s$ at the position given by $s$. 
\par

Let $S$ be a set, $a$ a positive natural number, 
and $\Phi$ a group of permutations over 
$[a]$. Then $\Phi$ acts naturally over
$S^a$ in the following way: Given $g\in \Phi$ and
$\overline{x}:=(x_1,\dots,x_a)\in S^a$ we define 
$g\cdot \overline{x}$ 
as the tuple $(x_{g(1)},\dots,x_{g(a)})$. 
We will denote by $S^a/\Phi$ to the quotient
of the set $S^a$ by this action. Given an element
$\overline{x}:=(x_1,\dots, x_a)\in S^a$ we denote its equivalence
class in $S^a/\Phi$ by $[x_1,\dots,x_a]$ or $[\overline{x}]$.
Thus, for any
$g\in \Phi$, by definition $[x_1,\dots,x_a]=[x_{g(1)}
,\dots,x_{g(a)}]$. \par
The notations $\overline{x}$ and
$(x_1,\dots, x_a)$ 
represent
ordered tuples while 
$[\overline{x}]$ and
$[x_1,\dots,x_a]$ denote ordered tuples modulo the
action of some arbitrary group of permutations. Which group is
this will depend on the ambient set where $[x_1,\dots,x_a]$ belongs
and it should either be clear from context or not be relevant.\par

Given real functions over the natural numbers 
$f,g:\N \rightarrow \R$ the expressions $f=O(g)$,
$f=o(g)$ and $f=\Theta(g)$ will have their usual meaning.
If $g(n)\neq 0$ for $n$ large enough then
we will write $f\sim g$ when $\Ln \frac{f(n)}{g(n)}=1$. \par

%%\todo[inline]{Añadir referencias y trabajo relacionado con random SAT}
%
\subsection{Probabilistic preliminaries}

We assume familiarity with basic probability theory. 
We denote by $\mathrm{Poiss}_\lambda(n)$ the discrete probability mass
function of a random variable following a Poisson distribution with
mean $\lambda$. That is, $\mathrm{Poiss}_\lambda(n)=e^{-\lambda}\frac{\lambda^n}{n!}$.
We define $\mathrm{Poiss}_\lambda(\geq n)=1 - \sum_{i=0}^{n-1} \mathrm{Poiss}_\lambda(i)$. \par

Our main tool for proving the convergence in distribution 
to Poisson variables ones is the next result, which can
be found in \cite[Theorem 1.23]{bollobas2001random}.

\begin{theorem} \label{thm:BrunSieve}
	Let $l\in \N$. For each 
	$n\in \N$, let $X_{n,1},\dots, X_{n,l}$ be non-negative
	random integer variables over the same
	probability space. Let $\lambda_1,\dots,\lambda_l$ 
	be real numbers. Suppose for any $r_1,\dots,r_l \in \N$
	\[ 
	\Ln \mathrm{E}\left[
	\prod_{i=1}^{l} \binom{X_{n,i}}{r_i} \right]
	= \prod_{i=1}^{l} \frac{\lambda_i}{r_i !}.	
	\]
	Then the $X_{n,1},\dots,X_{n,l}$ converge in distribution to
	independent Poisson variables with means $\lambda_1,\dots,\lambda_l$ 
	respectively. 
\end{theorem}

If $A,B$ are events we may write the conditioned probability $\mathrm{Pr}(A\, | \, B )$ 
as $\mathrm{Pr}_B(A)$ in some situations to shorten some expressions.

\subsection{Logical preliminaries}
We assume familiarity with first order logic (FO). We follow 
the convention that first order logic contains the equality symbol. 
Given a vocabulary $\sigma$ we will denote by $FO[\sigma]$ the set of 
first order formulas of vocabulary $\sigma$. We define the set of 
\textbf{free variables} of a formula as usual. 
Given a relation symbol $R\in \sigma$ we denote by $ar(R)$ the arity of $R$. 
Given a formula $\phi\in FO[\sigma]$ we will use the notation $\phi(\overline{y})$ 
to express that $\overline{y}$ is a tuple of 
(different) variables which contains all free variables in $\phi$ and
none of its bounded variables, but it may contain variables
which do not appear in $\phi$.
Formulas with no free variables are called \textbf{sentences} and 
formulas with no quantifiers are called \textbf{open formulas}. 
We call \textbf{edge sentence} to any consistent open formula that contains
no occurrence of the equality symbol `$=$'.

@@

We define the \textbf{excess} $ex(G)$ of an hypergraph $G$ as the number
\[
ex(G):= \left(\sum_{R\in \sigma} (ar(R)-1)|E_R(G)|\right) - |V(G)|.  
\] 
That is, the excess of $G$ is its "weighted number of edges"
minus its number of vertices. \par
An hypergraph $G$ is \textbf{connected} if for any two vertices $v,u\in V(G)$
there is a sequence of edges $e_1,\dots, e_m\in E(G)$ such that
$v\in V(e_1), u\in V(e_m)$ and for each $i\in [m-1]$, 
$V(e_i)\cap V(e_{i+1})\neq \emptyset$. It holds that
$ex(G)\geq -1$ for any connected hypergraph.
\par
Given an hypergraph $G$ we define the following metric, $d$, over $V(G)$:
\[ d^G(u,v)= \min_{\substack{H \subset G\\ 
		H \text{ connected }\\
		u,v\in V(H)}} |E(H)| .\]
That is, the \textbf{distance} between $v$ and $u$ is the minimum number of
edges necessary to connect $v$ and $u$. 
If such number does not exist we define $d^G(u,v)=\infty$. 
When $G$ 
is understood or not relevant we will usually simply denote the 
distance by $d$ instead of $d^G$. Equivalently, the distance $d$
coincides with the usual one defined over the Gaifman graph of the structure 
$G$. The \textbf{diameter} of an hypergraph is the maximum distance between any 
two of its vertices. 
We extend naturally the distance $d$ to sets and tuples of
vertices, as usual. Given a vertex/set/tuple $X$ and a number
$r\in \N$ we define the \textbf{neighborhood}
$N^G(X;r)$, or simply $N(X;r)$ when $G$ is not relevant,
as the set of vertices $v$ such that $d^G(X,v)\leq r$.
\par
A connected hypergraph $G$ is a \textbf{path} between two of its 
vertices $v,u\in V(G)$ if $G$ 
does not contain any connected proper sub-hypergraph containing both $v,u$.
\par
A connected hypergraph $G$ is a \textbf{tree} if $ex(G)=-1$ and \textbf{dense} if $ex(G)>0$.
An hypergraph is called $r$-\textbf{sparse} if it does not contain any dense sub-hypergraph $H$
such that $diam(H)\leq r$.
A connected hypergraph $G$ with $ex(G)\geq 0$ is called \textbf{saturated} 
if for any non-empty proper sub-hypergraph
$H\subset G$ it holds $ex(H)<ex(G)$. 
A connected hypergraph $G$ with $ex(G)=0$ is called \textbf{unicycle}. 
A saturated unicycle is called a \textbf{cycle}. \par
A \textbf{rooted tree} $(T,v)$ is a tree $T$ with a 
distinguished vertex $v\in V(T)$ called its \textbf{root}.
We will usually omit the root when it is not relevant and 
write just $T$ instead of $(T,v)$. The
\textbf{initial edges} of a rooted tree $(T,v)$ are 
the edges in $T$ that contain $v$. 
We define the radius of a rooted tree
as the maximum distance between its root
and any other vertex.
\par

@@

\textbf{Isomorphisms} between hypergraphs are defined the same as 
isomorphisms between relational structures. Isomorphisms between $\Sigma$-hypergraphs are just
isomorphisms between the underlying hypergraphs that also preserve their colorings. 
In both cases we denote the isomorphism relation by $\simeq$. 
Given an hypergraph $H$, resp. a $\Sigma$-hypergraph $(H, \chi)$,
an \textbf{automorphism} of $H$, resp. $(H,\chi)$,
is an isomorphism from $H$, resp. $(H,\chi)$, to itself.
We will denote by $\aut(H)$, resp. $\aut(H,\chi)$,
 the number of such automorphisms. \par

Let $H$ be an hypergraph and let $V$ be a set. We define the
set of \textbf{copies of $H$ over $V$}, denoted as $Copies(H,V)$, 
as the set of hypergraphs 
$H^\prime$ such that
$V(H^\prime)\subset V$ and $H\simeq H^\prime$. Let 
$\chi$ be a $\Sigma$-coloring of $H$. 
Analogously, we define the set $Copies\left(
(H,\chi),\, \, V\right)$ as the set of $\Sigma$-hypergraphs
$(H^\prime,\chi^\prime)$ satisfying $V(H^\prime)\subset V$ and
$(H,\chi)\simeq (H^\prime,\chi^\prime)$. Let $\mathbb{H}$ be 
an isomorphism class of $\Sigma$-hypergraphs. Then the set
$Copies(\mathbb{H}, V)$ is defined as the set of $\Sigma$-hypergraphs
$(H^\prime,\chi^\prime)$ such that 
$V(H^\prime)\subset V$ and
$(H^\prime,\chi^\prime)\in \mathbb{H}$. 
Let $v\in V$ and $s\in \Sigma$. We define the
set $Copies\left(\mathbb{H}, V;\,\, (v,s)\right)$ 
as the set of $\Sigma$-hypergraphs
$(H^\prime,\chi^\prime)\in Copies(\mathbb{H}, V)$
that satisfy $v\in V(H^\prime)$ as well as
$\chi^\prime(v)=s$. \par

Given $\mathbb{H}$ an isomorphism class of hypergraphs or $\Sigma$-hypergraphs,
we define expressions
such as $ex(\mathbb{H})$, $\aut(\mathbb{H})$,
$|V(\mathbb{H})|$, $|E(\mathbb{H})|$ or
$Copies(\mathbb{H},V)$ via representatives of $\mathbb{H}$.\par

@@

For any $k\in \N$ we define an equivalence relation over rooted trees
which generalizes both the relation of "$k$-morphism" as 
defined in \cite{lynch1992probabilities},
and the notion of "$(k,r)$-values" defined in \cite{salvadorbrasil}.

\begin{definition}\label{def:sim_trees}

@@

\begin{definition}
	Let $k,r\in\N$ and let $\Sigma_{(k,r)}$ 
	be the set of $\sim_k$ classes
	of rooted trees with radii at most $r$. Then
	we call a $(k,r)$-\textbf{cycle} to an isomorphism class
	of $\Sigma_{(k,r)}$-hypergraphs 
	$(H,\tau)$ that are cycles of diameter at most $2r+1$.
	We will denote by $C(k,r)$ the set of $(k,r)$-cycles.
\end{definition}
